Databrary: Enabling sharing and reuse of research video

### 2015-04-16 jcdl-15/demo.tex
some words

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often has a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study.
Session-level metadata might include participant details, conditions of study, tasks in the experiment, permission levels, study groups, or conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managing data in their own labs, making the interface and functionality intuitive to users.

@@

In addition, because video data involving human subjects is identifiable, we have built the access checks necessary to honor the participant consents under which the data were collected. 
User registration for gaining access to Databrary involves an authorization process by which site users are verified to be faculty, students, or researchers affiliated with an educational institution.
Users are required to review and sign an access agreement stating that they will treat the data they are able to access through Databrary in a manner that complies with the ethical handling of research data involving human subjects\footnote{http://databrary.org/access/policies/agreement.html}.
Finally, contributors are offered permission levels for files and groups of files that allow them to fine-tune who has access to their data.

>>>>

Focusing on a particular research domain allows us to develop tools informed by how the intended community of users currently works, while accommodating the specific privacy concerns for data that often have a high disclosure risk.
We have created a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
These features include a spreadsheet interface for entering, editing, and viewing the metadata for all sessions related to a study.
Session-level metadata might include participant details, conditions of study, tasks in the experiment, permission levels, study groups, or conditions, and serves the purpose of providing ways to browse and search for specific video data in Databrary. 
We have found that most researchers use desktop spreadsheets for managing data in their own labs, making the interface and functionality intuitive to users.

@@

In addition, because video data involving human subjects is identifiable, we have built the access checks necessary to honor the participant consents under which the data were collected. 
User registration for gaining access to Databrary involves an authorization process by which site users are verified to be faculty, students, or researchers affiliated with an educational institution.
Users are required to review and sign an access agreement stating that they will treat the data they are able to access through Databrary in a manner that complies with the ethical handling of research data involving human subjects\footnote{http://databrary.org/access/policies/agreement.html}.
Finally, contributors are offered the ability to set permission levels for files and groups of files that allow them to fine-tune who has access to their data.
